---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# topodetective

<!-- badges: start -->
<!-- badges: end -->

The goal of topodetective is to infer topology of species interactions from time series of species abundance. We use a regression-based method, which can efficiently enumerate all possible topologies.

## Installation

You can install the development version of InferInteractions from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("clsong/InferInteractions")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r warning=F, message = F, dpi=300 }
library(tidyverse)
library(topodetective)

get_classic_dynamics("4_species_chaos") # choose a population dynamic
time_range <- seq(0, 50, by = .1)

set.seed(12345)
ts <- generate_time_series_LV(
  topology = topology_ground,
  state_initial = state_initial,
  time_range = time_range,
  noise = T,
  noise_level = .05
) # simulate a dynamic

plot_time_series(ts)
```
We then infer system parameters from time series alone. We choose all possible topologies.
```{r}
reg_model <- choose_regression_model("linear")

fitted_models <- ts %>%
  differentiate_ts() %>%
  group_split(species) %>%
  map(fit_interaction_parameters) %>%
  bind_rows(.id = 'species') %>%
  mutate(species = paste0("x", species))
```

We then simulate the dynamics with the inferred parameters. We compare the fit.
```{r, dpi=300}
set.seed(123)
topology_fitted <- fitted_models %>%
  group_by(species) %>%
  top_n(3, R2) %>% 
  sample_n(1) %>%
  ungroup()

ts_simu <- simualte_fitted_dynamics(topology_fitted)
evaluate_fit(ts, ts_simu)

plot_true_vs_simu(ts, ts_simu)
```

# ```{r dpi = 300}
# library(ggraph)
# plot_interaction_topology(topology_ground, title = 'Groundtruth') +
#   plot_interaction_topology(topology_fitted, title = 'Fitted')
# ```

